\documentclass[a4paper,10pt]{article}
% Ensure proper encoding and modern fonts
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\usepackage[top=0.75in, bottom=0.75in, left=0.5in, right=0.5in]{geometry}
\usepackage{titlesec, enumitem, hyperref, xcolor, microtype, parskip}
\setlength{\parindent}{0pt}
\renewcommand{\baselinestretch}{1.1}

% Allow extra stretch to reduce underfull hbox warnings
\setlength\emergencystretch{3em}

% Define colors and hyperlink style
\definecolor{darkblue}{RGB}{0,102,204}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=darkblue}

% Section formatting with a subtle rule
\titleformat{\section}{\large\bfseries\color{darkblue}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\bfseries}{}{0em}{}
\setlist[itemize]{leftmargin=*, itemsep=2pt, topsep=0pt}

\begin{document}
% Note: Please compile directly with pdflatex/xelatex/lualatex (avoid pandoc conversion).

\begin{center}
    {\Huge \textbf{Túlio Ribeiro dos Anjos}} \\[1mm]
    {\large \textbf{Full-Stack .NET \& Cloud Developer}} \\[2mm]
    \textcolor{darkblue}{Campo Grande, Mato Grosso do Sul, Brazil} \\[1mm]
    \href{mailto:mail@tulio.org}{mail@tulio.org} \quad | \quad 
    \href{https://www.linkedin.com/in/tulioanjos}{linkedin.com/in/tulioanjos} \quad | \quad
    \href{https://tulio.org}{tulio.org} \quad | \quad +55 67 9 9266 0804
\end{center}
\vspace{2mm}
\hrule
\vspace{4mm}

% Main content: Two-column layout using minipages
\begin{minipage}[t]{0.65\textwidth}
\sloppy
    \section*{Summary}
    Full-stack .NET \& Cloud Developer specializing in designing scalable, high-performance applications. Experienced in modernizing legacy systems, integrating with e-commerce platforms, and optimizing cloud-based architectures using .NET 8, AWS Lambda, and Spring Boot. Passionate about solving complex engineering challenges and improving system efficiency.
    
    \vspace{4mm}
    \section*{Key Achievements}
    \begin{itemize}
        \item Developed an AWS Lambda-based \textbf{Shopify integration} in .NET 8, enabling a new direct-to-consumer sales channel and supporting \textbf{100,000+ SKU inventory synchronization}.
        \item Designed and implemented a \textbf{real-time image processing system} (AWS Lambda, .NET 8, SkiaSharp) for generating collages, reducing processing time and enhancing product previews.
        \item Built a \textbf{sales reporting service} leveraging JSON schema and CSVHelper, automating data ingestion from multiple payment platforms to improve auditability and accuracy.
        \item Transformed a \textbf{legacy JSF application} into a modern Angular 13 micro-frontend with a Spring Boot backend, \textbf{enhancing UI performance and maintainability}.
        \item Developed a \textbf{custom Java CLI tool} to automate \textbf{ETL and database provisioning} for government audits, integrating data from Sybase, Firebird, PostgreSQL, and MySQL.
        \item Eliminated a \textbf{CPU bottleneck} in a \textbf{real-time emergency dispatch system}, optimizing WebSocket vehicle tracking and improving dispatcher responsiveness.
    \end{itemize}
    
    \vspace{4mm}
    \section*{Experience}
    \subsection*{BairesDev (3 years)}
    \textbf{Full-Stack .NET \& Angular Engineer} \hfill \textit{Feb 2025 – Present}
    \begin{itemize}
        \item Building full-stack components for a next-generation transit management platform using .NET 8, Angular, and cloud-native architectures.
    \end{itemize}
    
    \textbf{.NET Core Engineer} \hfill \textit{Mar 2023 – Feb 2025}
    \begin{itemize}
        \item Developed a high-scale AWS Lambda-based Shopify integration (.NET 8), supporting 100,000+ SKUs and enabling seamless direct-to-consumer transactions.
        \item Implemented intelligent API throttling (data diffing \& retry), reducing failure rates.
        \item Created a high-performance image processing system (AWS Lambda, .NET 8, SkiaSharp) for real-time collage generation, achieving sub-second response times.
    \end{itemize}
    
    \subsection*{GEOI2 Tecnologia da Informação LTDA. (3 years)}
    \textbf{Software Engineer} \hfill \textit{Aug 2019 – Jun 2022}
    \begin{itemize}
        \item Revitalized a sluggish JSF system into a high-performance Angular 13 micro-frontend with a Spring Boot backend, improving UI speed and maintainability.
        \item Developed a Java CLI tool to automate ETL and database provisioning for Tribunal de Contas audits, integrating multiple databases and optimizing transmission over low-bandwidth networks.
    \end{itemize}
    
    \subsection*{Fonte Tecnologia (2 years)}
    \textbf{Software Developer} \hfill \textit{Aug 2017 – Aug 2019}
    \begin{itemize}
        \item Eliminated a critical CPU bottleneck in CADG’s real-time vehicle grid by optimizing WebSocket responsiveness for emergency dispatch operations.
        \item Built a high-efficiency telephone form module for emergency call incident reporting, improving dispatcher workflows.
    \end{itemize}
\end{minipage}
\hfill
\begin{minipage}[t]{0.32\textwidth}
\raggedright
    \section*{Skills}
    \begin{itemize}
        \item .NET 8 Full-Stack Development (Angular, ASP.NET Core, WebAPI)
        \item Cloud Computing (AWS Services: Lambda, Serverless Architectures)
        \item REST API Design \& Optimization
        \item Performance \& Scalability Engineering
    \end{itemize}
    
    \vspace{4mm}
    \section*{Education}
    \textbf{Uniderp} \hfill \textit{Bachelor’s in Computer Engineering, Jan 2009 – Dec 2013}
    
    \vspace{4mm}
    \section*{Certifications}
    Oracle Certified Java SE 11 Developer
    
    \vspace{4mm}
    \section*{Languages}
    English: Professional Proficiency
\end{minipage}

\end{document}
